Beyesian Inference for Decision Making under COVID-19: A case study

### 2020-05-30 out/paper.Rmd
Sección VI draft

[^7]: All normal conjugacy cases are weel documented in **Insertar cita**.

@@

In spite of sections IV and V proposals we may still want to try some other "out the box" solution, for example fitting a Gamma distribution to the data. Either way we take numerical methods will be needed.

>>>>

[^7]: All normal conjugacy cases are wel documented in: Murphy. *Conjugate analysis of the Gaussian distribution*. 2007. Avaible [here](https://www.cs.ubc.ca/~murphyk/Papers/bayesGauss.pdf)

@@

In spite of sections IV and V proposals we may still may want to try some other "out the box" solution, for example fitting a log-Normal distribution to the data. Although in this case the classical approach offers an analytical solution through MLE, the output will lack, again, the robustness to incorporate COVID-19 diminished $\theta$ hypotheisis. On the other hand if we take the bayesian way we still have a conjugate case for the known variance case, however gong beyond that hypothesis would requiere numerical methods, in particular, Markov Chain Monte Carlo stochastics simulation.

Although, at first, this may look as a downside, abandoning conjugate schemes to MCMC methdos, if proceding with cuation, give us an amazing improvement in modeling flexibility.

For our last example lets consider $X_{i} \sim logNormal(x | \theta,\sigma^2)$ with $f(\theta) \sim \Gamma(\theta | \alpha, \beta)$ and $f(\sigma^2) \sim \Gamma^{-1}(\sigma^2 | a, b)$

**EL CASO LOGNORMAL ES UNA JALADA PERO ESTÁ MUY BUENO LO PUEDES ENCONTRAR DOCUMENTADO AQUÍ (SE HIZO CON R)** https://projecteuclid.org/download/pdfview_1/euclid.ba/1354024469
